SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-04-18 SI.tex

\begin{figure}[!h]
    \centering
    \includegraphics[width = \textwidth]{Figures/permeationSI.pdf}
    \caption{Water permeation through membranes analyzed from the Databank as a function of (A) hydration level, (B) fraction of cholesterol, (C) fraction of charged lipids, and (D) fraction of POPE in membrane. Values from simulations with non-zero permeation values are shown with blue dots. Histogrammed values are shown with black dots.
    }
    \label{fig:permeationSI}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width = \textwidth]{Figures/permeationSI.pdf}
    \caption{Water permeation through membranes analyzed from the Databank as a function of (A) hydration level, (B) fraction of cholesterol, (C) fraction of charged lipids, and (D) fraction of POPE in membrane. Values from simulations with non-zero permeation values are shown with blue dots. Histogrammed values are shown with black dots For the mean value in each bin, average weighted with the simulation lengths was used, and error bars show the standard error of the mean. Only bins with more than one microsecond of data were used. Only simulations with the temperatures between 300-315\,K were used.
    }
    \label{fig:permeationSI}
\end{figure}
